---
title: "VAST Challenge 2021 Mini-Challenge 2"
description: |
  Visual Analytics for VAST Challenge 2021 Mini-Challenge 2
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# 1 Background

## 1.1 Overview

Many of the Abila, Kronos-based employees of GAStech have company cars which are approved for both personal and business use. Those who do not have company cars have the ability to check out company trucks for business use, but these trucks cannot be used for personal business.

Employees with company cars are happy to have these vehicles, because the company cars are generally much higher quality than the cars they would be able to afford otherwise. However, GAStech does not trust their employees. Without the employees? knowledge, GAStech has installed geospatial tracking software in the company vehicles. The vehicles are tracked periodically as long as they are moving.

This vehicle tracking data has been made available to law enforcement to support their investigation. Unfortunately, data is not available for the day the GAStech employees went missing. Data is only available for the two weeks prior to the disappearance.

To promote local businesses, Kronos based companies provide a Kronos Kares benefit card to GASTech employees giving them discounts and rewards in exchange for collecting information about their credit card purchases and preferences as recorded on loyalty cards. This data has been made available to investigators in the hopes that it can help resolve the situation. However, Kronos Kares does not collect personal information beyond purchases.

## 1.2 Requirment

We must cope with uncertainties that result from missing, conflicting, and imperfect data to make recommendations for further investigation.

Use visual analytics to analyze the available data and develop responses to the questions below.

## 1.3 Tasks and Questions

1.  Using just the credit and loyalty card data, identify the most popular locations, and when they are popular. What anomalies do you see? What corrections would you recommend to correct these anomalies? Please limit your answer to 8 images and 300 words.

2.  Add the vehicle data to your analysis of the credit and loyalty card data. How does your assessment of the anomalies in question 1 change based on this new data? What discrepancies between vehicle, credit, and loyalty card data do you find? Please limit your answer to 8 images and 500 words.

3.  Can you infer the owners of each credit card and loyalty card? What is your evidence? Where are there uncertainties in your method? Where are there uncertainties in the data? Please limit your answer to 8 images and 500 words.

4.  Given the data sources provided, identify potential informal or unofficial relationships among GASTech personnel. Provide evidence for these relationships. Please limit your response to 8 images and 500 words.

5.  Do you see evidence of suspicious activity? Identify 1- 10 locations where you believe the suspicious activity is occurring, and why Please limit your response to 10 images and 500 words.

# 2 Methodology

## 2.1 Most Popular Locations

### 2.1.1 Data Preparation

```{r echo = FALSE}
library(ggplot2)
library(tidygraph)
library(ggraph)
library(igraph)
library(lubridate)
library(plotly)
library(ggiraph)
library(raster)
library(sf)
library(tmap)
library(clock)
library(tidyverse)
library(rgdal)
```

We firstly need to import the two csv file containing credit card and loyalty card transaction data.

```{r echo = TRUE}
cc_data <- read_csv("cc_data.csv")
loyalty_data <- read_csv("loyalty_data.csv")
```

In order to count credit card transaction and loyalty card transaction together, cc_data and loyalty_data is merged to get an overall transaction_data.

```{r echo = TRUE}
transaction_data = merge(cc_data, loyalty_data, all=TRUE)
```

### 2.1.2 Visualization

The total number of transactions at different locations are displayed by a bar chart. In order to sort the location name by their sales respectively, we write a re-order function to sort the y-axis.

```{r echo = TRUE}
reorder_size <- function(x) {
  factor(x, levels = names(sort(table(x))))
}      

ggplot(data = transaction_data, 
       aes(y = reorder_size(location))) + 
  geom_bar(color = "black",
           fill = "light blue") + 
  theme(axis.text.x = element_text(angle = 270)) + 
  xlab("Number of Transactions") + 
  ylab("Location") 
```

A heatmap is used here to show the distribution of transactions in different days to detect the peak hour of different shops.

```{r echo = TRUE}
name <- names(sort(table(transaction_data$location), decreasing = TRUE)[1])

most_pop <- cc_data[cc_data$location == name,]
most_pop$timestamp <- strptime(most_pop$timestamp, format='%m/%d/%Y %H:%M')

most_pop <- most_pop %>%
  mutate(most_pop, hour = strftime(most_pop$timestamp, format='%H')) %>%
  mutate(most_pop, day = strftime(most_pop$timestamp, format='%d'))

groups <- group_by(most_pop, day, hour)
values = summarise(groups, n())

ggplot(data = values, 
       aes(x = hour,
           y = day,
           fill = `n()`)) + 
  geom_raster() + 
  labs(fill = "Number of Orders")
```

Since we want to detect anomalies in these locations, we not only cares about their total sales but also want to know the account of each order. A box plot is designed to show the distribution of price of each order.

```{r echo = TRUE}
most_pop_transaction <- transaction_data[transaction_data$location == name,]
most_pop_transaction$timestamp <- strptime(most_pop_transaction$timestamp, format='%m/%d/%Y')
most_pop_transaction <- most_pop_transaction %>%
  mutate(most_pop_transaction, day = strftime(most_pop_transaction$timestamp, format='%m/%d'))

ggplot(data = most_pop_transaction, 
       aes(x = day,
           y = price)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_point(position = "jitter", 
             size = 1) + 
  theme(axis.text.x = element_text(angle = 270)) + 
  xlab("Day") + 
  ylab("Price")
```

## 2.2 Matching credit card and loyalty













# 3 Visualization

# 4 Answer













